\documentclass[twocolumn]{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{color}
\usepackage{soul}
\usepackage[bookmarks,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=blue]{hyperref}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{placeins}

\begin{document}

\title{IP-Controlled Low Voltage DC Power Distribution Unit\\ADVANCE SPECIFICATION}
\author{Andrew Zonenberg\\
	\texttt{azonenberg@drawersteak.com}}
\date{\today}
\maketitle

\fancyhead[L]{ADVANCE SPECIFICATION}
\fancyfoot[L]{$Revision$ / \today}
\pagestyle{fancy}

\setcounter{tocdepth}{3}
\tableofcontents

\section{Introduction}

\subsection{Overview}
The PDU is an intelligent power distribution system for a large number (up to ten) of low voltage DC loads, such as 
encountered in a development board cluster for embedded prototyping. It is intended to consolidate many ``wall wart" 
power supplies into a single unit supplied by an external high-efficiency supply, saving outlet and workbench space 
while providing additional management and safety capabilities.

\subsection{Feature summary}

\begin{itemize}
\item All functions of the device are accessible via SNMP using the on-board 10/100/1000 Mbps Ethernet port.
\item Each output channel is individually switched to permit remote reset of a malfunctioning board.
\item Per-channel current metering allows real-time monitoring (up to 20 KSa/s sampling rate per channel) of current 
consumed by downstream loads, providing instant feedback when optimizing DUT firmware for power.
\item Board-level reverse voltage protection guards against incorrect hookup of the upstream supply.
\item Input rail voltage is monitored internally and all outputs are disabled if the voltage deviates from nominal by 
more than a set threshold. A jumper on the board allows 5V or 12V mode to be selected and prevents damaging downstream 
devices if the PDU is accidentally connected to the wrong supply.
\item Two chassis temperature monitors allow thermal shutdown in the event of overload.
\item Programmable overcurrent shutdown for extremely rapid ($\mu s$ or less) shutdown of a shorting or malfunctioning
DUT. This protection responds significantly faster than a fuse and can be remotely reset once the fault condition has 
been cleared. Firmware allows flexible tailoring of overcurrent shutdown behavior including response time; a separate 
power-on threshold prevents false triggering from inrush currents.
\item Ten 3.3V  digital GPIO pins are provided for interfacing with external systems.
\item The entire system design (hardware and firmware) is released under a permissive open source license (3-clause
BSD). KiCAD design files and firmware source are available at \url{https://code.google.com/p/azonenberg-devboards/}
under the  subproject ``pdu-5v-20a". Modified firmware may be loaded onto the system via the provided JTAG header.
\end{itemize}

\section{Legal}

\subsection{Notes}

This is an advance specification of a system which is still under development. Some specifications are subject to 
change.

\subsection{License and disclaimers}
                                                                                                                   
Copyright (c) 2012-2013 Andrew D. Zonenberg. All rights reserved.

Redistribution and use in source, bitstream, or layout form, with or without modification, is permitted
provided that the following conditions are met:

\begin{itemize}
\item Redistributions of source code must retain the above copyright notice, this list of conditions, and the following
disclaimer.

\item Redistributions in bitstream or layout form must reproduce the above copyright notice, this list of conditions and
the following disclaimer in the documentation and/or other materials provided with the distribution.

\item Neither the name of the author nor the names of any contributors may be used to endorse or promote products
derived from this hardware or software without specific prior written permission.

\item THIS SOFTWARE AND HARDWARE DESIGN IS PROVIDED BY THE AUTHOR "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, 
INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE 
DISCLAIMED. IN NO EVENT SHALL THE AUTHOR BE HELD LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR 
CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, 
DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, 
STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE OR 
HARDWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\end{itemize}

\end{document}


